\documentclass{article}
\def\mytitle{Vijay Saraswat Resume}
%\usepackage{html,htmllist}
\usepackage{epsfig}
%begin{latexonly}
%\usepackage{url}
\usepackage{fancyheadings}
\input{pagesizes}
\pagestyle{fancy}
\usepackage{lastpage209}
\headrulewidth 0.0in
\footrulewidth 0.0in
\rhead{}
\lhead{}
\rfoot{Page \thepage\ of \pageref{LastPage} Saraswat Short Resume}
\bigskip
\usepackage{ssiarticle}
%\end{latexonly}

\begin{document}
%\begin{htmlonly}
%<p align=right><a href="resume.pdf">printable pdf version</a></p>
%\end{htmlonly}

\begin{center}
{\bf \sc Vijay Anand Saraswat}\\
\end{center}

\section*{Education}
\textit{Ph.D} Computer Science, Carnegie Mellon University, January 1989;
\textit{M.S.} Computer Science, Carnegie Mellon University, 1985.
\textit{B.Tech.} Electrical Engineering, Indian Institute of Technology,
   Kanpur, India, 1982.

\section*{Employment and other work}

Waseda University (Tokyo) Global COE Visiting Professor; 
\textit{Manager, Advanced Programming Languages and Research Staff Member}, IBM TJ Watson Research Center;
\textit{Professor of Computer Science and Engineering}, Penn State University;
\textit{Vice President, Engineering}, Kirusa, Inc;
\textit{Chief Technology Officer and Director, Development}, Vayusphere, Inc;
\textit{Technology Leader, Instant Messaging and Presence, District Manager, Principal Member, Technical Staff}, AT\&T Shannon Labs; 
\textit{Member, Research Staff}, Xerox Palo Alto Research Center;
\textit{Artifical Intelligence Scientist}, Carnegie Group Inc;
\textit{Consultant}, Carnegie Group Inc, Pittsburgh.

\section*{Academic awards and Industry recognition}

HPC Challenge Award (Type II) for X10 (2007, 2006); 
``Most influential paper in 20 years in Concurrent
Constraint Programming'' award from the Association of Logic
Programming for POPL90 paper;
Invited Expert of the W3C Working Group on Multi-Modal
Interaction; 
Co-Chair of the Working Group on Presence and Instant Messaging
(PRIM), Instant Messaging and Presence Protocols (IMPP), at IETF;
Excellence in Research Award, Xerox PARC;    
ACM Doctoral Dissertation Award for the best Computer Science
PhD Thesis in 1989;
Ratan Swaroop Gold Medal for all-round excellence,
      Indian Institute of Technology, Kanpur; 
Merit Scholarship for being the top-ranked student in the
      ``core'' (first 2.5/5) years  at IIT; 
Ranked 6th (out of $> 60,000$) in the Joint Entrance Exam
      for all the IITs;  

\section*{Research Grants}
\textit{Testing of hybrid and reactive systems}, 1 yr, \$150K NASA, 1994-1995; 
\textit{Timed Concurrent Constraint Programming}, 2 yrs, \$120K, ONR, 1994--1996;
\textit{Articulate Spaces:
   Model-based authentic environments for Collaborative Learning}, 2
   yrs, \$2m ARPA, Department of Defense, 1995-1997.
\textit{Collaborative learning spaces}, NSF, 1 year, 1996-97.

\section*{Theses}
{\bf Thesis Co-Advisor}
\textit{Clifford Tse} ``Linear Janus'' (Master's thesis 1992, MIT
  Laboratory for Computer Science) MIT-PARC VI-A student; Co-advisor with Bill Dally.

{\bf Committee member}
\textit{Francesca Rossi} (PhD 1993, University of Pisa) 
(Advisor: Ugo Montanari);
\textit{Eric Torng} (PhD 1994, Stanford University) (Advisor: Rajeev Motwani);
\textit{Paul Ruet} (PhD 1996, University of Paris) (Advisor: Francois Fages);
\textit{Venkatesh Mysore} (PhD 2005, New York University) (Advisor: Bud Mishra);
\textit{Carlos Olarte} (PhD 2009 forthcoming, Ecole Polytechnique, Paris) (Advisor: Catuscia Palamidessi, Frank Valencia).

\section*{Books}
Proceedings of ASIAN 03, ed.{} Vijay Saraswat, Springer Verlag
LNCS 2896;
Constraint Programming: The Newport Papers, ed.{} Vijay
Saraswat and Pascal van Hentenryck, MIT Press, 1995;
Proceedings of the 1991 International Symposium on Logic
  Programming, ed.{} Vijay Saraswat and Kazunori Ueda, MIT Press,
  1991;
Vijay Saraswat ``Concurrent Constraint Programming'' MIT
  Press Logic Programming and Doctoral Dissertation Award Series,
  1991.

\section*{Edited journal issues}
Vijay Saraswat, Pascal van Hentenryck Special issues of
  CONSTRAINTS on Strategic Directions in Constraint Programming,
  February 1997;
Pascal van Hentenryck, Vijay Saraswat, ed. ``Constraint
  Programming'', in Special Issue of Computing Surveys on
  Strategic Directions in Computer Science, February 1997.

\section*{Selected Publications}
\subsection*{X10}
\begin{itemize}
\item Ganesh Bikshandi, Jose Castanos, Sreedhar Kodali, Krishna Nandivada, Igor Peshansky, Vijay Saraswat, Sayantan Sur, Pradeep Varma, Tong Wen ``Efficient, Portable Implementation of Asynchronous Multi-place Programs'', PPoPP 2009.

\item Maged Michael, Martin Vechev and Vijay Saraswat ``Idempotent Work stealing'', PPoPP 2009.

\item Nathaniel Nystrom, Vijay Saraswat, Jens Palsberg and Christian
Grothoff ``Constrained types for OO Languages'', OOPSLA
2008.

\item Guojing Cong, Sreedhar Kodali, Sriram Krishnamoorthy, Doug Lee,
Vijay Saraswat and Tong Wen ``Solving irregular graph problems using
adaptive work-stealing'', ICPP 2008.

\item Vijay Saraswat, Radha Jagadeesan, Maged Michael and Christoph
von Praun, ``A Theory of Memory Models'', Proceedings of the ACM
Symposium on Principles and Practice of Parallel Programming, March
2007.

\item Philippe Charles, Christian Grothoff, Kemal Ebcioglu, Allan
  Kielstra, Christoph von Praun, Vijay Saraswat and Vivek Sarkar
  ``X10: An Object-oriented Approach to Non-Uniform Cluster
  Computing'', Onwards! Track of the Proceedings of OOPSLA 2005.

\item Vijay Saraswat and Radha Jagadeesan ``Concurrent Clustered
  Programming'', Proceedings of CONCUR, 2005.

\end{itemize}				   

\subsection*{Semantic foundations for concurrent programming}
\begin{itemize} 

\item Catuscia Palamidessi, Vijay Saraswat, Frank Valencia and Bjorn
Victor ``On the expressiveness of linearity and persistence in the
pi-calculus'', LICS 2006.

\item Radha Jagadeesan and Gopalan Nadathur and Vijay Saraswat
``Testing concurrent systems: An interpretation of intuitionistic
logic'', Proceedings of FST\&TCS, December 2005.

\item Vijay Saraswat ``Constraint-Based Memory Machines: A framework
for Java Memory Models'', ASIAN 2004, pp 494-508.

\item  Vijay Saraswat ``The category of constraint systems is
  Cartesian-closed'', Proceedings of the Symposium on Logic in
  Computer Science, Santa Cruz, June 1992.

\item  Vijay Saraswat and Rinard M. and Panagaden, P. ``Semantic
  foundations for concurrent constraint programming'', \textit{
  Proceedings of the ACM Symposium on Principles of Programming
  Languages}, Orlando, January 1991.
  
\item  Vijay Saraswat and Rinard, M. ``Concurrent constraint
  programming'', Proceedings of the ACM Symposium on
  Principles of Programming Languages 1990, San Fransisco, January
  1990.

\item  Vineet Gupta, Radha Jagadeesan and Vijay Saraswat
  ``Computing with Continuous Change'',  Science of
  Computer Programming, 30 (1:2) 3-49, 1998.

\item  Markus Fromherz, Vijay Saraswat and Daniel G. Bobrow
  ``Model-based computing: Developing flexible machine control
  software'', Artificial Intelligence, 114(1-2): 157-202 (1999)

\item Introduction. (Mary Dalrymple, Fernando Pereira, John Lamping,
   Vijay Saraswat) In \textit{Semantics And Syntax in Lexical Functional
   Grammar: The Resource Logic Approach} edited by Mary Dalrymple. The
   MIT Press, 1999.

\item Vijay Saraswat ``Java is not type-safe'', Web-note
  \texttt{http://www.research.att.com/~vj/bug.html}. Described a major
  bug in the design of the class-loader mechanism. This was
  acknowledged and fixed by Sun in a major redesign. See Bracha and
  Liang's paper in OOPSLA 98.

\item Pascal van Hentenryck, Yves Deville, Vijay Saraswat ``Design,
    implementation and evaluation of the constraint language cc(FD)'',
    Journal Of Logic Programming 37(1-3):139-164 (1998). Conference
    paper in LNCS 910, pp 293-316 (1994).

\item Armando Solar-Lezama, Gilad Arnold, Liviu Tancau, Ratislav
Bodik, Vijay Saraswat and Sanjit Seshia ``Sketching Stencils'', in ACM
SIGPLAN Conference on Programming Language Design and Implementation
(PLDI '07).

\item   Rajeev Motwani, Suresh Venkatsubramaniam, Rina Panigrahy, Vijay
   Saraswat ``On the decidability of accessibility problems'', ACM
   Symposium on the Theory of Computing, 2000.

\end{itemize}


\end{document}